\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-08-07 doc/sw-system.tex
Added agent histories plot, fixes #37

\Fref{fig:agent-probabilities} shows random selection of Agents' confusion
matrix elements, as they were on a particular day towards the end of the
CFHTLS project. Many volunteers classify  only a small number of images, and
so their Agents' confusion matrix elements remain close to their initial
values of (0.5,0.5). As more images are classified (shown by the yellow point
size), the Agents' matrix elements tend to move towards higher values, as the
volunteers attain greater skill levels (green point sizes, see
\Sref{sec:results} below) and the Agent learns more about them. In this
quadrant, the Agents perceive their volunteers to be ``astute.''

@@

\todo{Phil}{Include agent histories plot, discuss}

>>>>

\Fref{fig:swap:agent-probabilities} shows a random selection of Agents'
confusion matrix elements, as they were on a particular day towards the end of
the CFHTLS project. Many volunteers classify  only a small number of images,
and so their Agents' confusion matrix elements remain close to their initial
values of (0.5,0.5). As more images are classified (shown by the yellow point
size), the Agents' matrix elements tend to move towards higher values, as the
volunteers attain greater skill levels (green point sizes, see
\Sref{sec:results} below) and the Agent learns more about them. In this
quadrant, the Agents perceive their volunteers to be ``astute.'' This trend is
more clearly seen in \Fref{fig:swap:agent-histories}, which shows the skill of
the same sample of Agents as the number of images classified increases. The
histogram shows the distribution of classification number: a long tail to very
high ``effort'' can be seen.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
\caption{Typical \SW Agent histories. The ``skill'' of the  same 200 random
Agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
of the number  of subjects classified (``effort''). The yellow histogram in
the background shows the distribution of effort.}
\label{fig:swap:agent-histories}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
